### 2025-08-10 evaluating-prediction-accuracy.qmd
20250810 - accuracy at cutoff

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `petersenlab::accuracyAtCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables.

```{r}
#petersenlab::accuracyAtCutoff()
```

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `petersenlab::accuracyAtEachCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables at each possible cutoff.

```{r}
#petersenlab::accuracyAtEachCutoff()
```

>>>>

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `petersenlab::accuracyAtCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables.
In the example below, we compute the accuracy of predictions for which Running Backs or Wide Receivers will score 300 or more fantasy points, using a cutoff for average projected fantasy points of 300.

```{r}
petersenlab::accuracyAtCutoff(
  predicted = projectionsWithActuals_seasonal_subset$raw_points,
  actual = projectionsWithActuals_seasonal_subset$truth,
  cutoff = 300
)
```

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `petersenlab::accuracyAtEachCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables at each possible cutoff.
In the example below, we compute the accuracy of predictions for which Running Backs or Wide Receivers will score 300 or more fantasy points, at each possible cutoff for average projected fantasy points.

```{r}
petersenlab::accuracyAtEachCutoff(
  predicted = projectionsWithActuals_seasonal_subset$raw_points,
  actual = projectionsWithActuals_seasonal_subset$truth
)
```
